---
title: "Observer-deployed TDR trip summary"
header-includes:
- \usepackage{tabto}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: pdf_document
classoption: landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
```

```{r, message = FALSE}
# Load libraries
library(tidyverse, quietly = TRUE)
library(here)
library(lubridate)
```

```{r}
############################## Acknowledgements ##############################
# This code is based off of Johanna Wren's code for Cooperative Research 
# trip reports.  Thanks, Johanna!
##############################################################################
```

```{r}
# This section builds out some fields to construct the file name
# and populates some values we'll use again

# Enter the trip number here
TripNum <- c('LL')

# Enter trip type here (deep or shallow)
TripType <- c('DeepSet')

# Enter TDR nomenclature here (deep/shallow or 1/2)
TDRa <- c('DeepTDR')
TDRb <- c('ShallowTDR')
```

```{r}
# Load data, and add a column for gear position
# This is written for a Mac and things are probably different on a PC
tdr1 <- read_csv(paste("/Volumes/GUTSNGRAVY/ObserverTDRs/",
                       TripNum, "_",
                       TripType, "_",
                       TDRa, ".csv", sep = ""),
                 skip = 2, show_col_types = FALSE) |>
  mutate(GearPos = "Deep")

tdr2 <- read_csv(paste("/Volumes/GUTSNGRAVY/ObserverTDRs/", 
                       TripNum, "_",
                       TripType, "_",
                       TDRb, ".csv", sep = ""),
                 skip = 2, show_col_types = FALSE) |>
  mutate(GearPos = "Shallow")

# Combine data, noting deep and shallow or 1 and 2
tdr <- bind_rows(list(tdr1, tdr2))
```

```{r}
# Deal with the dates
tdr$Time <- as.character(tdr$Time)
tdr$DateTime <- as.POSIXct(paste(tdr$Date, tdr$Time), format="%m/%d/%Y %H:%M:%S")
```

```{r}
# We'll need to trim off the surface data at the very least, and we can modify this bit depending on what the data look like
# Here I'm replacing the surface values with NA otherwise the data plots poorly
# Observer TDRs: I've tested a few values for shallow sets (11, 5, 0.5) and they
# all look the same so I went with least restrictive value
tdr <- tdr %>% 
  mutate(DepthOnly=replace(`Pressure [dBars]`, `Pressure [dBars]` <= 0.5, NA))
```

## Trip Number `r TripNum`, `r TripType`
The following plot shows the depth of the gear (vertically) over time 
(horizontally) from the TDRs.  The color of the line is the temperature at the 
depth of the gear.  The stacked appearance is because 2 TDRs are attached to 
each set.  You're seeing the temperature and depth reported by each of these 
TDRs - 'shallow' and 'deep' - together in one figure.
<!-- The following plot shows the depth of gear (vertically) over time (horizontally)
from the TDRs.  The TDRs appear to have failed at some point on the trip.  One
only shows surface values after the 12th set.  We were unable to get data off
of the second TDR.  -->
<!-- The following plot shows the depth of the gear (vertically) over time
(horizontally) from the TDRs.  One TDR was lost at sea (it happens), and the 
remaining shallow TDR was only deployed for three sets. -->

```{r, fig.height=4, fig.width=9}
# Set custom ggplot theme for all figures for uniform look in the report
tdrTheme <- theme_bw() + 
            theme(panel.grid=element_blank(),
                  #legend.key.height = unit(2, "cm"),
                  legend.title = element_text(size = 12, angle = 90),
                  legend.title.align = 0.5,
                  legend.direction = "vertical")

# Make a simple depth time series
ggplot(tdr, aes(DateTime, DepthOnly, color=`IntTemp [C]`)) +
  geom_path() + 
  scale_color_viridis_c('Water Temperature (°C)', option = 'turbo') + #,
                        # limits = c(10,32)) +
  scale_x_datetime(date_labels='%d-%b-%Y', date_breaks = '2 days') + 
                   # limits = c(
                   #   as.POSIXct("2025-09-24 00:00:00 HST"),
                   #   as.POSIXct("2025-10-13 00:00:00 HST"))) +
  scale_y_reverse() +
  xlab('Date') +
  ylab('Depth (m)') +
  tdrTheme +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  guides(colour=guide_colourbar(title.position = 'right', barheight=17))
```
<!-- \newpage

This plot shows the same thing, only it's limited to the upper 10 meters of the
the water so you can see the data better.  
```{r, message = FALSE, fig.height=4, fig.width=9}
# Adding and additional plot to focus on the shallowest depths, since there's
# one really deep one.

# Make a simple depth time series
ggplot(tdr, aes(DateTime, DepthOnly, color=`IntTemp [C]`)) +
  geom_path() + 
  scale_color_viridis_c('Water Temperature (°C)', option = 'turbo') +
  scale_x_datetime(date_labels='%d-%b-%Y', date_breaks = '2 days', ) +
  scale_y_reverse() +
  xlab('Date') +
  ylab('Depth (m)') +
  ylim(10, 0) +
  tdrTheme +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  guides(colour=guide_colourbar(title.position = 'right', barheight=17))
```

