---
title: "TDRmetadata"
author: "phoebe.woodworth-jefcoats@noaa.gov"
date: "2024-12-17"
output: html_document
---

The purpose of this script is to update the metadata record for the Observer deployed TDRs. The script appends the newest TDR information to the google sheet, then overwrites the old .csv metadata file for submission to NCEI. 

```{r}
# Set up environment
library(tidyverse, quietly = TRUE)
library(googledrive)
library(googlesheets4)
library(here)
```

This is written for a Mac and things may be different on a PC.  

The data is housed 'locally' on a Shared Google Drive, so the script works completely within the GutsNGravy shared drive.  

```{r}
# This section builds out some fields to construct the file name
# and populates some values we'll use again

# Enter the trip number here
TripNum <- c('LL8804')

# Enter trip type here (deep or shallow)
TripType <- c('DeepSet')

# Enter TDR nomenclature here (deep/shallow or 1/2)
TDRa <- c('TDR1')
TDRb <- c('TDR2')

# Type in any comments from the observers
obsComsA <- "Crew had difficulty understanding placement of the clips. Some of the TDRs were deployed 1-2 (beeps) hooks away from directed location."
obsComsB <- "Crew had difficulty understanding placement of the clips. Some of the TDRs were deployed 1-2 (beeps) hooks away from directed location."

# Type in any comments you might have about the data
dataComsA <- "TDRs kept recording while in the case so cut the data after the last set"
dataComsB <- "TDRs kept recording while in the case so cut the data after the last set"

# Path to TDR drive
tdrDrive <- '~/Google Drive/Shared drives/NMFS PIC ESD PRP GutsNGravy/ObserverTDRs'
```

If you are using Drive 4 Desktop use this code chunk
(Wild card search for file names doesn't work in Google Drive)
```{r include=FALSE}
# Paste the file name together and fine the matching file
tdrAfile <- Sys.glob(file.path(tdrDrive, paste0('TDR_', TripNum, '_', TDRa, '_*.csv')))
tdrBfile <- Sys.glob(file.path(tdrDrive, paste0('TDR_', TripNum, '_', TDRb, '_*.csv')))

# Read in the TDR files
tdr1 <- read_csv(tdrAfile, show_col_types = F)
tdr2 <- read_csv(tdrBfile, show_col_types = F)
```

If you don't have Drive 4 Desktop, this allows code chunk allows you to access straight from the shared GutsNGravy file
```{r eval=FALSE, include=FALSE}
# Authorize google drive
drive_auth()

# Make the file names
tdrName <- paste0("^TDR_", TripNum, "_", TDRa, "_.*\\.csv$")

# Find the files in google drive
tdrFile <- drive_find(
    pattern = tdrName,
    shared_drive = "NMFS PIC ESD PRP GutsNGravy",
    corpus = "drive"
)

# Read in (stream) the file directly into memory 
tdr1 <- read_csv(drive_read_string(tdrFile[1,]), show_col_types = FALSE) |>
  mutate(GearPos = "Shallow")
tdr2 <- read_csv(drive_read_string(tdrFile[2,]), show_col_types = FALSE) |>
  mutate(GearPos = "Deep")
```

The TDRs keep collecting data until they dry, which can take a while in the 
pelican case.  So, filtering to get only records with a valid flag of 1.
If negative pressures are present, I filter those out, too.
```{r}
tdr1 <- tdr1 |>
  filter(`Valid Flag` == 1)  |>
  filter(`Pressure [dBars]` > 0.75)

tdr2 <- tdr2 |>
  filter(`Valid Flag` == 1)  |>
  filter(`Pressure [dBars]` > 0.75)
```

We can append the metadata directly to a google sheet, so we are creating dataframes below with all the needed information and then pushing it to the metadata file. 
```{r}
# Prepare a dataframe with the new TDRs metadata.
# I'm doing one data frame for each TDR instead of combining them. 
new_row_TDR1 <- data.frame(
  FileName = basename(tdrAfile),  # or if you used the google drive method above tdrAfile$name
  TripID = TripNum,
  TripType = TripType,
  HookDepth = ifelse(mean(tdr1$`Pressure [dBars]`) < mean(tdr2$`Pressure [dBars]`), 'Shallow', 'Deep'),
  StartDate_HST = min(tdr1$Date, na.rm = T),
  EndDate_HST = max(tdr1$Date, na.rm=T),
  ObserverComments = obsComsA,
  DataComments = dataComsA
)

# Prepare a dataframe with the new TDRs metadata
new_row_TDR2 <- data.frame(
  FileName = basename(tdrBfile), # or if you used the google drive method above tdrBfile$name,
  TripID = TripNum,
  TripType = TripType,
  HookDepth = ifelse(mean(tdr2$`Pressure [dBars]`) > mean(tdr1$`Pressure [dBars]`), 'Deep', 'Shallow'),
  StartDate_HST = min(tdr2$Date, na.rm = T),
  EndDate_HST = max(tdr2$Date, na.rm=T),
  ObserverComments = obsComsB,
  DataComments = dataComsB
)

new_rows <- rbind(new_row_TDR1, new_row_TDR2)

```

Append the newest data to the metadata file
```{r}
# authenticate
gs4_auth()

# Append the last TDR trip information
sheet_append(
  ss = "1qDbJCz7SZlEK47RZR6Bs24tsvUHD5tE2ttvKQhC4iu4", # This is the PIROP_TDR_metadata google sheet ID. It doesn't change so can be hardcoded in
  data = new_rows
)
```

Save the metadata file as a .csv for NCEI to GutsNGravy shared drive
This file needs to be submitted with the TDR files each time. 

If you have Drive for Desktop
```{r}
# Fetch the updated metadata sheet
updated_metadata_sheet <- read_sheet(ss ="1qDbJCz7SZlEK47RZR6Bs24tsvUHD5tE2ttvKQhC4iu4")

# Save locally in your google drive
write.csv(updated_metadata_sheet, file = file.path(tdrDrive, 'PIORP_TDR_metadata.csv'), row.names = FALSE, quote = F)
```

If you are working directly in Google Drive (a bit more cumbersome)
```{r eval=FALSE, include=FALSE}
# Fetch the updated metadata sheet
updated_metadata_sheet <- read_sheet(ss = "1qDbJCz7SZlEK47RZR6Bs24tsvUHD5tE2ttvKQhC4iu4")

# Save locally to a temporary CSV file
temp_csv <- tempfile(fileext = ".csv")
write.csv(updated_metadata_sheet, file = temp_csv, row.names = FALSE)

# Save/Upload the CSV directly to Google Drive
# First, locate the Shared Drive named "GutsNGravy" to get the ID
guts_drive <- shared_drive_find(pattern = "NMFS PIC ESD PRP GutsNGravy")
observer_folder <- drive_find(
    pattern = "^ObserverTDRs$",
    type = "folder",
    shared_drive = guts_drive
)

# Use drive_put() to create the file or overwrite/update it if it already exists
drive_put(
  media = temp_csv,
  path = observer_folder,
  name = "PIROP_TDR_metadata.csv",
)

# Clean up local temporary file
file.remove(temp_csv)

```


