---
title: "TDRmetadata"
author: "phoebe.woodworth-jefcoats@noaa.gov"
date: "2024-12-17"
output: html_document
---

The purpose of this script is to collect the start and end date for the observer-
collected TDR data.

```{r}
# Set up environment
library(tidyverse)
```

This is written for a Mac and things may be different on a PC.  
```{r}
# Load data
tdr1 <- read_csv("/Volumes/GUTSNGRAVY/ObserverTDRs/LL8516_ShallowSet_TDR1.csv", skip = 2, show_col_types = FALSE)
tdr2 <- read_csv("/Volumes/GUTSNGRAVY/ObserverTDRs/LL8516_ShallowSet_TDR2.csv", skip = 2, show_col_types = FALSE)
```

The TDRs keep collecting data until they dry, which can take a while in the 
pelican case.  So, filtering to get only records with a valid flag of 1.
If negative pressures are present, I filter those out, too.
```{r}
tdr1 <- tdr1 |>
  filter(`Valid Flag` == 1) |>
  filter(`Pressure [dBars]` > 0)

tdr2 <- tdr2 |>
  filter(`Valid Flag` == 1)  |>
  filter(`Pressure [dBars]` > 0)
```

I just run head() and tail() in the console and then copy/paste the first/last
value into the metadata sheet.

When copy and pasting the dates into the Excel metadata sheet, I precede the text
with an apostrophe so that Excel doesn't try to do its own thing with the dates.

