---
title: "TDRmetadata"
author: "phoebe.woodworth-jefcoats@noaa.gov"
date: "2024-12-17"
output: html_document
---

The purpose of this script is to update the metadata record for the Observer deployed TDRs. The script appends the newest TDR information to the google sheet, then overwrites the old .csv metadata file for submission to NCEI. 

```{r}
# Set up environment
library(tidyverse, quietly = TRUE)
library(googledrive)
library(googlesheets4)
library(here)
```

This is written for a Mac and things may be different on a PC.  

The data is housed 'locally' on a Shared Google Drive, so the script works completely within the GutsNGravy shared drive.  

```{r}
# This section builds out some fields to construct the file name
# and populates some values we'll use again

# Enter the trip number here
TripNum <- c('LL8804')

# Enter trip type here (deep or shallow)
TripType <- c('DeepSet')

# Enter TDR nomenclature here (deep/shallow or 1/2)
TDRa <- c('TDR1')
TDRb <- c('TDR2')

```

```{r include=FALSE}
# Authorize google drive
drive_auth()
```

```{r include=FALSE}
# Make the file names
# Shallow
tdrAname <- paste0("ObserverTDRs/", TripNum, "_", TripType, "_", TDRa, ".csv")
# Deep
tdrBname <- paste0("ObserverTDRs/", TripNum, "_", TripType, "_", TDRb, ".csv")

# Find the files in google drive
# Shallow
tdrAfile <- drive_get(
  path = tdrAname, 
  shared_drive = "NMFS PIC ESD PRP GutsNGravy"
)
# Deep
tdrBfile <- drive_get(
  path = tdrBname, 
  shared_drive = "NMFS PIC ESD PRP GutsNGravy"
)

# Read in (stream) the file directly into memory 
tdr1 <- read_csv(drive_read_string(tdrAfile), skip = 2, show_col_types = FALSE) |>
  mutate(GearPos = "Shallow")
tdr2 <- read_csv(drive_read_string(tdrBfile), skip = 2, show_col_types = FALSE) |>
  mutate(GearPos = "Deep")
```

The TDRs keep collecting data until they dry, which can take a while in the 
pelican case.  So, filtering to get only records with a valid flag of 1.
If negative pressures are present, I filter those out, too.
```{r}
tdr1 <- tdr1 |>
  filter(`Valid Flag` == 1)  |>
  filter(`Pressure [dBars]` > 0.75)

tdr2 <- tdr2 |>
  filter(`Valid Flag` == 1)  |>
  filter(`Pressure [dBars]` > 0.75)
```

We can append the metadata directly to a google sheet, so we are creating dataframes below with all the needed information and then pushing it to the metadata file. 
```{r}
# Prepare a dataframe with the new TDRs metadata.
# I'm doing one data frame for each TDR instead of combining them. 
new_row_TDR1 <- data.frame(
  FileName = tdrAfile$name,
  TripID = TripNum,
  TripType = TripType,
  HookDepth = ifelse(mean(tdr1$`Pressure [dBars]`) < mean(tdr2$`Pressure [dBars]`), 'Shallow', 'Deep'),
  StartDate_HST = min(tdr1$Date, na.rm = T),
  EndDate_HST = max(tdr1$Date, na.rm=T),
  ObserverComments = "Crew had difficulty understanding placement of the clips. Some of the TDRs were deployed 1-2 (beeps) hooks away from directed location."
)

# Prepare a dataframe with the new TDRs metadata
new_row_TDR2 <- data.frame(
  FileName = tdrBfile$name,
  TripID = TripNum,
  TripType = TripType,
  HookDepth = ifelse(mean(tdr2$`Pressure [dBars]`) > mean(tdr1$`Pressure [dBars]`), 'Deep', 'Shallow'),
  StartDate_HST = min(tdr2$Date, na.rm = T),
  EndDate_HST = max(tdr2$Date, na.rm=T),
  ObserverComments = "Crew had difficulty understanding placement of the clips. Some of the TDRs were deployed 1-2 (beeps) hooks away from directed location."
)

new_rows <- rbind(new_row_TDR1, new_row_TDR2)

```

Append the newest data to the metadata file
```{r}
# authenticate
gs4_auth()

# metadata sheet url
meta_url <- "https://docs.google.com/spreadsheets/d/1qDbJCz7SZlEK47RZR6Bs24tsvUHD5tE2ttvKQhC4iu4/edit?usp=sharing"

sheet_append(
  ss = meta_url,
  data = new_rows,
  sheet = 1 # Sheet tab name or index (defaults to the first sheet)
)
```

Save the metadata file as a .csv for NCEI to GutsNGravy shared drive
This file needs to be submitted with the TDR files each time. 
```{r}
# Fetch the updated metadata sheet
updated_data <- read_sheet(ss = meta_url, sheet = 1)

# Save locally to a temporary CSV file
temp_csv <- tempfile(fileext = ".csv")
write.csv(updated_metadata_sheet, file = temp_csv, row.names = FALSE)

# Save/Upload the CSV directly to Google Drive
# First, locate the Shared Drive named "GutsNGravy" to get the ID
guts_drive <- shared_drive_find(pattern = "NMFS PIC ESD PRP GutsNGravy")
observer_folder <- drive_find(
    pattern = "^ObserverTDRs$",
    type = "folder",
    shared_drive = guts_drive
)

# Use drive_put() to create the file or overwrite/update it if it already exists
drive_put(
  media = temp_csv,
  path = observer_folder,
  name = "PIROP_TDR_metadata.csv",
)

# Clean up local temporary file
file.remove(temp_csv)

```


